%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\usepackage{enumitem}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Łukasz Leszko}}}} % First name
	
	\vspace{6pt}
	
	{\Large ML Engineer} % Career or current job title
    \\[12pt]
    \small{Preferred locations: Warsaw, remotely or short-term abroad.}
\end{minipage}
\hfill
\begin{minipage}[t]{0.27\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% \icon{Globe}{11}{\href{http://www.google.com}{portafolio.com}}\\ 
    \icon{Phone}{11}{+48 ... }\\ %691 885 163}\\
    \icon{Envelope}{11}{\href{mailto:leszko.lucas@gmail.com}{leszko.lucas@gmail.com}}\\	
    \icon{Home}{11}{\href{https://lukasz.leszko.dev/}{lukasz.leszko.dev}}\\

    % \icon{MapMarker}{11}{City, Country}\\
	
\end{minipage}
\begin{minipage}[t]{0.2\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
    \icon{Github}{11}{\href{https://github.com/leszkolukasz}{leszkolukasz}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/leszkolukasz}{leszkolukasz}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
	Student at the University of Warsaw with a strong background in competitive programming and \textbf{1 year} of professional software development experience. Knowledgeable about applying machine learning to real-world projects, such as \textbf{Git Optim} and \textbf{QUMAM}. Solid foundation in mathematics and driven to apply technical expertise to high-impact solutions.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.50\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.15\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.75\textwidth}
    %   \textsl{Good knowledge of}: Java, Python, C++, TypeScript, HTML, CSS, SQL.\\
    %   \textsl{Basic knowledge of}: Kotlin, Rust, OCaml, Haskell, R.
    Python, C++, Rust, Haskell, TypeScript, Java
    \end{minipage}
    \vspace{2mm}
    
    \begin{minipage}[t]{0.15\textwidth}
        \textbf{ML:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.75\textwidth}
      PyTorch, Transformers, ONNX, scikit-learn, NumPy, Polars
    \end{minipage}
    \vspace{2mm}

    \begin{minipage}[t]{0.15\textwidth}
        \textbf{Web:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.75\textwidth}
      React, Django, FastAPI, Spring
    \end{minipage}
    \vspace{2mm}

    \begin{minipage}[t]{0.14\textwidth}
        \textbf{DevOps:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.76\textwidth}
     Docker, Google Cloud, Nix
    \end{minipage}
\end{minipage}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{\phantom}
		{Git Optim}
		{}
		{Developed as part of my Bachelor's thesis in Computer Science. Web application that utilizes Large Language Models (\textbf{LLMs}) to monitor CI/CD pipelines for warnings and errors in job logs. Upon detection, it automatically creates pull request with suggested fixes.\\[2mm]
        \texttt{Python, Accelerate, Llama.cpp, ChromaDB, TypeScript, Next.js, FastAPI}}
    \entry
		{\phantom}
		{\underline{\href{https://qumam.edu.pl}{QUMAM}}}
		{}
		{Learning platform for managing math courses and students. It offers rich UI for creating courses and exercises, as well as a student portal for tracking progress. Includes \textbf{LLM} capabilities like math task generation from image.\\[2mm]
        \texttt{Python, LiteLLM, OpenAI, TypeScript, React, Django, PostgreSQL}}
    \entry
		{}
		{\vspace{-3mm}}
		{}
		{Many more projects are available in my \underline{\href{https://lukasz.leszko.dev/}{portfolio}} and \underline{\href{https://github.com/leszkolukasz}{GitHub profile}}.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-15pt}
\cvsect{Experience}
\begin{entrylist}
    \entry
        {7/2024 -- 10/2024}
		{Junior Software Engineer}
		{RadCode, Warsaw}
		{
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Worked as a contractor for an American startup founded by a Forbes 30 Under 30 laureate.
            \item Developed a Web3 protocol with goal to innovate decentralized finance (DeFi).
        \end{itemize}
        \vspace{2mm}
        \texttt{TypeScript, Solidity, ReactJS, Hardhat, Vite, GraphQL}
        }
	\entry
        {7/2023 -- 7/2024}
		{Junior Software Engineer}
		{Cognizant, Warsaw}
		{\\
        \textbf{\small Project 1}\\
        \vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Acted as a project lead, actively contributing to the development of an internal web application using the Kanban methodology.
            \item Successfully deployed version 2.0 of the application.
        \end{itemize}
        \vspace{2mm}
        \texttt{Java, Kotlin, Spring, Jenkins, TypeScript, ReactJS, Vite, MongoDB, SendGrid}
        \\\\
        \textbf{\small Project 2}\\
        \vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Worked as contractor for American company.
            \item Refactored and optimized the application's codebase to adhere to clean code standards.
            \item Integrated Kafka using outbox pattern for efficient message queuing and processing.
        \end{itemize}
        \vspace{2mm}
        \texttt{Java, Spring, GitHub Actions, TypeScript, ReactJS, PostgreSQL, Kafka}}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-15 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{2024 - current}
		{M.Sc. in Machine Learning}
		{University of Warsaw}
		{\textsl{Elective courses}: Data Mining, Engineering Distributed Infrastructure, Robot Learning}
    \entry
		{2022 - current}
		{B.Sc. in Mathematics }
		{University of Warsaw}
		{\textsl{Relevant courses}: Statistical Data Analysis, Machine Learning (\textbf{GenAI})}
    \entry
		{2021 - 2024}
		{B.Sc. in Computer Science}
		{University of Warsaw}
		{\textsl{Relevant courses}: Machine Learning (classical methods)\\ \textsl{Thesis}: Gitoptim - a tool for automating programmer's work using large language models}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-15 pt}
	\cvsect{Achievements}
\vspace{-10 pt}
\begin{itemize}[parsep=0pt,partopsep=0pt,leftmargin=26mm]
    \item Distinction in the 1st round of the 28th Polish Olympiad in Informatics
    \item Finalist of the 4th edition of the Jagiellonian Mathematics Tournament
    \item Tutored two participants of Polish Olympiad in Informatics. One reached international level.
\end{itemize}
 

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\vspace{-7 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - B2/C1\hspace{3pt}(FCE Certificate), \textbf{ Polish} - native

\vspace{-5 pt}
	\cvsect{Interests}
    \vspace{-6pt}
    
    \begin{itemize}[topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=26mm]
    \item Open source: contributed to LibreOffice
    \item Programming languages (compilers, language design)
    \item Linux
\end{itemize}

\vspace*{\fill}

% Wyrażam zgodę na przetwarzanie moich danych osobowych dla potrzeb niezbędnych do realizacji obecnego procesu rekrutacji oraz przyszłych procesów rekrutacyjnych (zgodnie z ustawą z dnia 10 maja 2018 roku o ochronie danych osobowych (Dz. Ustaw z 2018, poz. 1000) oraz zgodnie z Rozporządzeniem Parlamentu Europejskiego i Rady (UE) 2016/679 z dnia 27 kwietnia 2016 r. w sprawie ochrony osób fizycznych w związku z przetwarzaniem danych osobowych i w sprawie swobodnego przepływu takich danych oraz uchylenia dyrektywy 95/46/WE (RODO)).

% I hereby give consent for my personal data to be processed by Jane Street for the purpose of conducting recruitment for the position for which I am applying.

%----------------------------------------------------------------------------------------

\end{document}
